Meta-analysis

### 2020-06-15 04_MetaAnalysis.Rmd
small corrections

   - Grain yield is our response variable and will be converted to Kg / Ha.  
   - Trial, which resolves combinations of categorical variables: year, location, row spacing and cultivar; is set as a random intercept.  
   - We will test spray management (our treatment) as a fixed effect and random slope to trial.

First lets compare models with and without a log transformed response variable to evaluate if the log transformed model better fits our assumptions of normality.  
Next we will test whether including `spray_management` as a significantly accounts for enough variation as a fixed effect variable to be included in the model.  
Finally we will test whether including `spray_management` as a significantly accounts for enough variation as a random slope to the trial variable.

@@

m11 <-
   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
           (1 | trial),
        data = slimmer_PM_dat)
```

@@

```{r Metafor-analysis}
PM_mv_AI <- rma.mv(
   yi,
   yield_error,
   mods = ~ spray_management,
   method = "ML",
   random = list(~ spray_management | trial),
   struct = "UN",
   data = slimmer_PM_dat
)

>>>>

   - Grain yield is our response variable and will be converted to Kg / Ha.  
   - Trial, which resolves combinations of categorical variables: year, location, row spacing, fungicide dose and cultivar; is set as a random intercept.  
   - We will test spray management (our treatment) as a fixed effect and random slope to trial.

First lets compare models with and without a log transformed response variable to evaluate if the log transformed model better fits our assumptions of normality.  
Next we will test whether including `spray_management` as a fixed effect variable significantly accounts for enough variation to be included in the model.  
Finally we will test whether including `spray_management`  as a random slope significantly accounts for enough variation to be used in the model.

@@

m11 <-
   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
           (1 | trial),
        data = slimmer_PM_dat)

@@

```{r Metafor-analysis}
PM_mv_AI <- rma.mv(
   yi,
   yield_error,
   mods = ~ spray_management,
   method = "ML",
   random = ~ 1|trial,
#   struct = "UN",
   data = slimmer_PM_dat
)
